---
title: "hw6"
author: "Junjie Hu"
date: "2023-12-01"
output: github_document
editor_options: 
  chunk_output_type: inline
---

```{r}
library(tidyverse)
library(purrr)
library(modelr)
library(mgcv)
```

# Problem 1
```{r}
homicide_df =
  read.csv("homicide-data.csv")|>
  janitor::clean_names() |>
  mutate(city_state = paste(city, state, sep = ",")) |>
  mutate(resolved = ifelse(disposition %in% c("Closed without arrest", "Open/No arrest"), "No", "Yes")) |>
   filter(city_state != "Tulsa,AL" & 
         city_state != "Dallas,TX" & 
         city_state != "Phoenix,AZ" & 
         city_state != "Kansas City,MO") |>
  filter(victim_race %in% c("White", "Black")) |>
  mutate(
    resolved = as.numeric(disposition == "Closed by arrest"),
    victim_age = as.numeric(victim_age),
    victim_race = fct_relevel(victim_race, "White")) |> 
  select(resolved, victim_age, victim_race, victim_sex, city_state)
```
Imported homicide data, created new variable `city_state` and `solved`, and omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO.


```{r}
baltimore_df =  
  homicide_df |>
  filter(city_state == "Baltimore,MD")


fit_logistic = 
  baltimore_df |> 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = _, family = binomial()) 

fit_logistic |> 
  broom::tidy(conf.int = TRUE) |> 
  mutate(OR = exp(estimate),
         conf.low = exp(conf.low),
         conf.high = exp(conf.high)) |>
  select(term, log_OR = estimate, OR, conf.low, conf.high, p.value) |> 
  knitr::kable(digits = 3)
  
```
Fit a logistic regression for the binary “resolved” outcome and victim demographics as predictors.

The odds of solving homicide among male victims is 0.426 times compared to the odds of female victims, adjusting for age and race. We are 95% confident that the true odds ratio falls between 0.324 and 0.558.

```{r}
model_results = 
  homicide_df |> 
  nest(data = -city_state) |> 
  mutate(
    models = map(data, \(df) glm(resolved ~ victim_age + victim_sex + victim_race, 
                             family = binomial(), data = df)),
    tidy_models = map(models, broom::tidy)) |> 
  select(-models, -data) |> 
  unnest(cols = tidy_models) |> 
  mutate(
    OR = exp(estimate), 
    OR_CI_upper = exp(estimate + 1.96 * std.error),
    OR_CI_lower = exp(estimate - 1.96 * std.error)) |> 
  filter(term == "victim_sexMale") |> 
  select(city_state, OR, OR_CI_lower, OR_CI_upper)

model_results |>
  slice(1:5) |> 
  knitr::kable(digits = 3)
```

```{r}
model_results |> 
  mutate(city_state = fct_reorder(city_state, OR)) |> 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = OR_CI_lower, ymax = OR_CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```
Imported data

```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}

boot_straps = 
  tibble(strap_number = 1:5000) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(df = weather_df))
  )

boot_straps
```
Prepared 5000 boot_straps sample for future analysis.

```{r}
bootstrap_results = 
  boot_straps |> 
  mutate(
    models = map(strap_sample, \(df) lm(tmax ~ tmin + prcp, data = df) ),
    glance = map(models, broom::glance),
    results = map(models, broom::tidy),
    log_product = map(models, ~log(abs(coef(.x)['tmin'] * coef(.x)['prcp'])))
    ) |> 
    select(-strap_sample, -models, -results) |> 
    unnest(cols = c(glance, log_product))

```
Produced estimates of these two quantities

```{r}
bootstrap_results |>
  ggplot(aes(x = r.squared)) +
  geom_density() +
  labs(title = "Distribution of r squared Estimates",
       x = "r squared",
       y = "Frequency") +
  theme_minimal()

bootstrap_results |>
  ggplot(aes(x = log_product)) +
  geom_density() +
  labs(title = "Distribution of Log_product Estimates",
       x = "Log_product",
       y = "Frequency") +
  theme_minimal()
```

```{r}
quantile(pull(bootstrap_results, r.squared), probs = c(0.025, 0.975)) |>
  knitr::kable(digits = 3)
```
Quantile for r.squared

```{r}
quantile(pull(bootstrap_results, log_product), probs = c(0.025, 0.975)) |>
knitr::kable(digits = 3)
  
```
Quantile for log_product

# Problem 3

```{r}
birthweight_df =
  read.csv("birthweight.csv")|>
  janitor::clean_names() |>
  mutate(
    babysex = recode(babysex,
                     "1" = "male",
                     "2" = "female"),
    frace = recode(frace,
                   "1" = "White",
                   "2" = "Black",
                   "3" = "Asian",
                   "4" = "Puerto Rican",
                   "8" = NA_character_,
                   "9" = NA_character_),
    malform = recode(malform,
                     "0" = "absent",
                     "1" = "present"),
    mrace = recode(mrace,
                   "1" = "White",
                   "2" = "Black",
                   "3" = "Asian",
                   "4" = "Puerto Rican",
                   "8" = NA_character_)
  ) |>
    mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) 
  
```
Converted numeric variables to factor and specified names. 
Those who answered "Others" and "Unknown" for father race is coded as missing and excluded from the regression.
Those who answered "Others" for mother race is coded as missing and excluded from the regression.


```{r}
unique(birthweight_df$pnumgsa)
unique(birthweight_df$pnumlbw)
```
Variables `pnumgsa` and `pnumlbw` are excluded from the analysis, because all observation is "0" for these two variables. 

```{r}
variables = c("babysex","bhead","blength","delwt","fincome","frace","gaweeks","malform","menarche","mheight","momage","mrace","parity","ppbmi","ppwt","smoken","wtgain")

fit_and_summarize <- function(var) {
  model = lm(as.formula(paste("bwt ~", var)), data = birthweight_df) |>
  
  broom::tidy()
}

model_summaries = 
  map(variables, fit_and_summarize) |>
  bind_rows() |>
  filter(p.value <= 0.05 & term != "(Intercept)")

model_summaries
```
Conducted bivariate analysis to identify the variables that are significantly associated with birth weight. The significant variables (p values <= 0.05) are included to the final multivariate model.

```{r}
fit_model = lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks 
                 + mheight + momage + mrace + ppbmi + ppwt + smoken + wtgain, data = birthweight_df)

```
Fitted the significant variables in bivariate analysis to a multivariate model.

```{r}
birthweight_df |> 
  modelr::add_residuals(fit_model) |> 
  modelr::add_predictions(fit_model) |>
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() +
  labs(title = "Model Residuals against Predicted Birth Weight",
       x = "Predicted Birth Weight",
       y = "Residual") +
  theme_minimal()
```

There is a few outliers. But, in general, the residual is evenly spread out around zero. Hence, the model should be able to successfully predict the birth weight.

```{r}
cv_df =
  crossv_mc(birthweight_df, 100) |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df |> 
  mutate(
    
    linear_1 = map(train, \(df) lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + mheight + momage + mrace + ppbmi + ppwt + smoken + wtgain, data = df)),
    
    linear_2 = map(train, \(df) lm(bwt ~ blength + gaweeks, data = df)),
    
    linear_3  = map(train, \(df) lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + bhead*babysex + bhead*blength*babysex, data = as_tibble(df)))
    ) |> 
  mutate(
    rmse_linear_1 = map2_dbl(linear_1, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_linear_2 = map2_dbl(linear_2, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_linear_3 = map2_dbl(linear_3, test, \(mod, df) rmse(model = mod, data = df)))
  
```


```{r}
cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  mutate(model = fct_inorder(model)) |> 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
  labs(title = "Model Comparasion",
       x = "Models",
       y = "RMSE") +
  theme_minimal()
```
My model have the lowest RMSE, following my model 3. The highest RMSE is model 2.

Linear 1: My model

Linear 2: Using length at birth and gestational age as predictors (main effects only)

Linear 3: Using head circumference, length, sex, and all interactions (including the three-way interaction)
